---
title: "webScrapperInR"
author: "Jay Gohner"
date: "October 29, 2019"
output: html_document
---

This will be a walkthrough and demonstration for a web scrapper using R. First we will load in the necessary libraries and
we will use the suppressMessages functions to keep the noise down!

We will begin with the in class example and build a templated function from that code that can then be used on other url's 
linking to CSUC schedule pages.

We create a variable called myurl and store the Spring 2019 schedule's url.
Then using an rvest function called read_html we can read in the html linked to by the url.
```{r}
suppressMessages(library("tidyverse"))
suppressMessages(library("rvest"))

myurl <- "http://ems.csuchico.edu/APSS/schedule/spr2019/CSCI.shtml"
spring2019_html <- read_html(myurl)

```

We build a function for each column we want to scrape and place in our newly created tibble.
This is accomplished using the function html_nodes to read in the specific node from the html and then we flatten the node
using html_text. In cases where necessary we use also use as.integer(). This is all strung together using R's piping method.
```{r}
spring2019 <- spring2019_html %>% 
                html_nodes("tr")

subject <- spring2019 %>% 
                html_nodes("td.subj") %>% 
                html_text()

class_num <- spring2019 %>% 
                    html_nodes("td.cat_num") %>% 
                    html_text()

section <- spring2019 %>% 
              html_nodes("td.sect") %>% 
              html_text() %>% 
              as.integer()

title <- spring2019 %>% 
          html_nodes("td.title") %>% 
          html_text()

unit <- spring2019 %>% 
            html_nodes("td.units") %>%
            html_text() %>%
            as.integer()

instructor <- spring2019 %>%
                html_nodes("td.Instructor") %>%
                html_text

capacity <- spring2019 %>%
                html_nodes("td.seatsavail") %>%
                html_text() %>%
                as.integer()

spring2019_print <- tibble(subjects = subject, class_nums = class_num, sections = section, units = unit, titles = title, instructors = instructor, enrollment = capacity)
```

Now that we know the above code does in fact scrape the information from the nodes that we want, we can refactor it to
accommodate any provided url.
```{r}
read_class_schedule <- function(the_url) {
  schedule <- read_html(the_url) %>% 
                html_nodes("tr")
  
  subject <- schedule %>% 
                html_nodes("td.subj") %>%
                html_text()

  class_num <- schedule %>% 
                  html_nodes("td.cat_num") %>% 
                  html_text()

  section <- schedule %>% 
                html_nodes("td.sect") %>% 
                html_text() %>% 
                as.integer()

  title <- schedule %>% 
              html_nodes("td.title") %>% 
              html_text()
  
  unit <- schedule %>% 
            html_nodes("td.units") %>%
            html_text() %>%
            as.integer()

  instructor <- schedule %>%
                    html_nodes("td.Instructor") %>%
                    html_text
  
  capacity <- schedule %>%
                html_nodes("td.seatsavail") %>%
                html_text() %>%
                as.integer()
  
  ##semester_year <- read_html(myurl) %>% 
    ##            html_nodes("#bd > div > div > h1") %>%
    ##            html_text()
  ##reg_pattern <- "(Fall|Spring)\ (\\d+)"
  
  ##temp <- stringr::str_match_all(semester_year, reg_pattern)
  
  ##(temp)
  
  ##semester_year <- schedule

sched_print <- tibble(subjects = subject, class_nums = class_num, sections = section, titles = title, units = unit, instructors = instructor, enrollment = capacity)
}
```

And as a demonstration we then scrape and print the four provided urls into one tibble.
```{r}
csci_spring_2019 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2019/CSCI.shtml")
csci_spring_2020 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2020/CSCI.shtml")
math_spring_2019 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2019/MATH.shtml")
math_spring_2020 <- read_class_schedule("http://ems.csuchico.edu/APSS/schedule/spr2020/MATH.shtml")

schedule_classes <- csci_spring_2019 %>%
                      full_join(csci_spring_2020) %>%
                      full_join(math_spring_2019) %>%
                      full_join(math_spring_2020)
                      
(schedule_classes)
```